\begin{rubric}{Selected Projects}

\entry*[2019 -- $\cdots\cdot$] % In development
	\textbf{ChatlogGrapher} \href{https://github.com/cephcyn/ChatlogGrapher}{(On GitHub)}
	\par Personal project
	\par Relevant skills: Python, Jupyter Notebook, word2vec, data cleaning
	\par Designed and implemented a wide variety of visualizations for text chat history data. \textit{ChatlogGrapher} is currently able to make use of Google Hangouts, Facebook Messenger, and Discord chat export data.
\entry*[2019 -- $\cdots\cdot$] % In development
	\textbf{cse517project} \href{https://github.com/cephcyn/cse517project}{(on GitHub)}
	\par Class project, research project, group project
	\par Relevant skills: Python, Jupyter Notebook, word2vec, LDA, BERT, Reddit post scraping, data cleaning
	\par Designed and implemented a replication of a published research paper. We scraped thousands of new posts from Reddit and conducted a comparison between different clustering methods, including methods based on word2vec, LDA, and BERT. \href{https://github.com/cephcyn/cephcyn.github.io/raw/master/documents/u_cse517/final_writeup.pdf}{Initial paper write-up} and \href{https://www.youtube.com/watch?v=SgzpiQQEeEU}{presentation} available, also being edited for submission for publication.
\entry*[2019 -- $\cdots\cdot$] % In development
	\textbf{familytree} \href{https://github.com/cephcyn/familytree}{(on GitHub)}
	\par Personal project, group project
	\par Relevant skills: SQL, TODO...
	\par Designed and implemented a family tree management program.
\entry*[2019 -- $\cdots\cdot$] % In development
	\textbf{hourglassQT} \href{https://github.com/cephcyn/hourglassQT}{(on GitHub)}
	\par Personal project
	\par Relevant skills: C++, QT
	\par Designed and implemented a simple cross-platform timer desktop application using QT.
\entry*[2020] % Complete / As-Is
	\textbf{"Examining Context-Aware Explanations for Recommender Systems"} % (CSE510)
	\par Class project, research project, group project
	\par Relevant skills: user research, interview analysis
	\par Interviewed students about their experiences finding research papers, as well as their thoughts on different styles of explanations from paper recommendation engines. \href{https://github.com/cephcyn/cephcyn.github.io/raw/master/documents/u_cse510/final_ContextExpl.pdf}{Paper write-up} is available.
\entry*[2020] % Complete / As-Is
	\textbf{Career Compass} % (CSE499 Entrepreneurship)
	\par Class project, group project
	\par Relevant skills: product design, user research, startup pitch design
	\par Designed and wrote a pitch for a startup that would offer career advice and serve as a mentoring program targeted at women.
\entry*[2019] % Paused (in planning)
	\textbf{DouDiZhu} \href{https://github.com/cephcyn/DouDiZhu}{(on GitHub)}
	\par Personal project
	\par Relevant skills: Java, Android development, TODO...
	\par Design and implementation of a Chinese card game ("fight the landlord") for Android devices. % Chinese name: 斗地主
\entry*[2019] % Complete / As-Is
	\textbf{xk operating system} % (CSE451)
	\par Class project, guided project, group project
	\par Relevant skills: C, assembly, low-level system interaction
	\par Implemented a basic OS (xk) using C. % TODO there's gotta be more detail I can put here?
\entry*[2019] % Complete / As-Is
	\textbf{Access, Period} % (CSE440)
	\par Class project, group project
	\par Relevant skills: product design, user research
	\par "Access, Period" product design focused on making menstrual products accessible for all, targeted specifically at homeless women in Seattle. The product concept is a phone app linked with a system of donation/pickup boxes located in public restrooms.
	\par Won "Most Innovative Solution" across the entire class!
\entry*[2019] % Complete / As-Is
	\textbf{"Finding and evaluating RNA motifs with CMfinder"} \href{https://github.com/cephcyn/jcmf}{(on GitHub)}
	\par Research project
	\par Relevant skills: Java, NCBI Genome track browser and resources
	\par Designed and implemented tools and pipeline centered on \textit{CMfinder} to search for potentially structured fRNA sequences across alignment block boundaries and cluster found covariance models. Paper write-up is available \cite{zhou2019thesis}.
\entry*[2019] % Paused (in planning)
	\textbf{TextAdventure} \href{https://github.com/cephcyn/TextAdventure}{(on GitHub)}
	\par Personal project
	\par Relevant skills: Java, TODO...
	\par Design and implementation of a rudimentary interactive fiction (IF) engine. The aim is to allow novices to write their own text-interface IF.
\entry*[2019] % Complete / As-Is
	\textbf{"A Computational Method of Bias Reduction in Allele-Specific Expression Analysis"} % (CSE428)
	\par Class (capstone) project, group project
	\par Relevant skills: Bash, Python, Java, NCBI Genome resources
	\par Designed and implemented a pipeline analysis using \textit{seqbias} to correct for RNA mapping count biases when evaluating allele-specific expression of different genetic sequences. \href{https://github.com/cephcyn/cephcyn.github.io/raw/master/documents/u_cse428/ASE_Report.pdf}{Paper write-up} and \href{https://github.com/cephcyn/cephcyn.github.io/raw/master/documents/u_cse428/ASE_Presentation.pptx}{presentation} also available.
\entry*[2019] % Complete / As-Is
	\textbf{SimpleDB} % (CSE444)
	\par Class project, guided project
	\par Relevant skills: Java
	\par Implementation of SimpleDB database in Java, including functionality such as buffer management, operators, transactions, recovery/rollback, and query optimization.
\entry*[2018] % Complete / As-Is
	\textbf{Twitter scraping} % \href{https://github.com/cephcyn/chocolate\_twitter\_scraping}{(on GitHub)}
	\par Research project
	\par Relevant skills: Python, Selenium, Tweepy, data cleaning
	\par Improved pre-existing Python utilities to scrape a large number of Twitter users' full tweet history into a standard format. Wrote guides for future researchers on how to use the tool.
\entry*[2018] % Complete / As-Is
	\textbf{Divided Congress \& Coverage} \href{https://cse442-18f.github.io/fp-divided-congress-and-coverage/}{(viewable online)} % (CSE442)
	\par Class project, group project
	\par Relevant skills: JavaScript, D3, data cleaning
	\par Designed, collected data for, implemented, and presented a set of visualizations together with commentary examining biases in news coverage between CNN, MSNBC, and Fox News on topics related to the 2016 U.S. presidential election.
	\par Won "Best In Show" across the entire class!
\entry*[2018] % Complete / As-Is
	\textbf{Smith-Waterman, HMM Viterbi, MEME utilities} % (CSE427)
	\par Class project
	\par Relevant skills: Java, NCBI Genome resources
	\par Designed and implemented Smith-Waterman sequence aligment, HMM/Viterbi G-C patch finding, and MEME-variant sequence-based motif discovery command-line utilities.
\entry*[2018] % Complete / As-Is
	\textbf{Flight search tool} % (CSE344)
	\par Class project, guided project
	\par Relevant skills: SQL, Java
	\par Designed a database to store information about flights. Designed and implemented a Java command-line tool to search for flights using this database.
\entry*[2018] % Complete / As-Is
	\textbf{Chess Bots} % (CSE332)
	\par Class project, guided project, group project
	\par Relevant skills: Java
	\par Implemented chess bots using minimax, parallel minimax, and alpha-beta algorithms.
\entry*[2018] % Complete / As-Is
	\textbf{333gle} % (CSE333)
	\par Class project, guided project
	\par Relevant skills: C, C++, file I/O, network I/O
	\par Implemented standard data structures (linked list, hash table) and used them for crawling, indexing, and searching plain-text files in a specified directory. Implemented part of a web server and interface to support this search tool.
\entry*[2018] % Complete / As-Is
	\textbf{Conway's Game of Life} % (CSE369)
	\par Class project
	\par Relevant skills: SystemVerilog, breadboard hardware prototyping
	\par Implemented Conway's Game of Life on a DE1-SoC hardware design board using SystemVerilog.
\entry*[2018] % Complete / As-Is
	\textbf{CampusPaths} % (CSE331)
	\par Class project, guided project
	\par Relevant skills: Java, Swing
	\par Implemented a map pathfinding utility to navigate between points on the UW campus using Java Swing API.
\entry*[2017] % Complete / As-Is
	\textbf{bio-evolution} \href{https://github.com/cephcyn/bio-evolution}{(on GitHub)}
	\par Personal project
	\par Relevant skills: Java, Swing
	\par Implemented a paper evolution simulation activity from AP Biology using Java Swing API.
\entry*[2017] % Complete / As-Is
	\textbf{RPG final project} % (ENGL242)
	\par Class project, group project
	\par Relevant skills: RPG design, narrative writing
	\par Designed an RPG ruleset and campaign as a reflection on Octavia Butler's novel Dawn.
\end{rubric}