\begin{rubric}{Teaching}

\entry*[2021 -- $\cdots\cdot$] % 2021nov - ...
    \textbf{EYH workshop leader/volunteer}, \href{https://www.eyh.cornell.edu/}{Expanding Your Horizons (EYH) @ Cornell University}
    \par EYH is a yearly conference hosted at Cornell designed to help grade school students explore STEM topics.
    \par The conference is hosted every spring. Planning begins in the previous fall semester.
    \par I often lead revisions of workshop mini syllabus, schedule, and activities in a team with 1-5 fellow volunteers.
    \par Taught groups of 5-25 students (6th to 10th grade), optionally including their buddy volunteers or parents.
\entry*[]
    2025: Program Your Own Animation! (intro to programming in Scratch)
\entry*[]
    2024: Program Your Own Animation! (intro to programming in Scratch)
\entry*[]
    2023: Program Your Own Animation! (intro to programming in Scratch)
\entry*[]
    2022: Googling with Paper Airplanes (intro to networking concepts)

\entry*[2018 -- 2021] % 2018apr - 2021aug
	\textbf{Teaching Assistant}, University of Washington Seattle
	\par Taught sections of 20+ students and assisted individual students in office hours.
	\par Wrote and reviewed course handouts, homework, and exams.
	\par Graded student programming assignments and exams.
\entry*[]
	2021 SU: CSE333 Systems Programming (\pWangC{})
\entry*[]
	2021 SP: CSE374 Programming Tools \& Concepts (\pHazenM{})
\entry*[]
	2021 WI: CSE417 Algorithms \& Computational Complexity (\pWeberR{})
\entry*[]
	2019 AU: CSE374 Programming Tools \& Concepts (\pPirtleT{})
\entry*[]
	2019 SP: CSE369 Introduction to Digital Design (\pHsiaJ{})
\entry*[]
	2019 WI: CSE369 Introduction to Digital Design (\pHsiaJ{})
\entry*[]
	2018 AU: CSE331 Software Design \& Implementation (\pErnstM{})
\entry*[]
	2018 SU: CSE331 Software Design \& Implementation (\pPerlmutterL{})

\entry*[2018]
	\textbf{Volunteer study group leader}, University of Washington
	\par Reviewed concepts taught in class with students.
\entry*[]
	2018 SP: CSE351 The Hardware/Software Interface

\entry*[2017]
	\textbf{Private tutor}
	\par Taught concepts in introductory Java programming to CS students outside of UW.
\end{rubric}